### 2018-04-22 README.Rmd
taxize as opt in  (#167)
* - replace Sxslt with xslt
- replace rrdf with librdf
- fix sparql vignette

* update docs

* update NEWS

* patch travis

* additional repositories not needed

[![DOI](https://zenodo.org/badge/11856817.svg)](https://zenodo.org/badge/latestdoi/11856817)
[![codecov.io](https://codecov.io/github/ropensci/RNeXML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/RNeXML?branch=master)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)

>>>>

[![DOI](https://zenodo.org/badge/11856817.svg)](https://zenodo.org/badge/latestdoi/11856817)
[![codecov.io](https://codecov.io/github/ropensci/RNeXML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/RNeXML?branch=master)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)
[![Coverage Status](https://img.shields.io/codecov/c/github/ropensci/RNeXML/master.svg)](https://codecov.io/github/ropensci/RNeXML?branch=master)
